---
title: "Summary Report"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, eval = TRUE, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE }
require(data.table)
require(dplyr)
require(ggplot2)
require(agricolae)
require(DT)
require(bit64)

fast_read <- function(dir, file)
{
  return(
    data.table::fread(file = paste0(dir, file)) %>% 
      rename(
        'Highest' = 'V1',
        'Sum' = 'V2',
        'Count' = 'V3',
        'Start' = 'V4',
        'End' = 'V5'
      ) %>%
      mutate(
        Script = substr(file, 1, nchar(file)-4),
        Interval = (End - Start)/1000000000
      )
  )
}
   

```


## Introduction

The goal of this report is to ...

`r if(Sys.getenv("EXPERIMENT_LABEL") != ""){paste("Experiment label: ", Sys.getenv("EXPERIMENT_LABEL"), ".")}` 

[Download output files](outputs.tar.gz)

## Descriptive

In this session will be presented the descriptive statistics about the time of execution of each programming language. 

**PS:** It was removed from the analysis the top and bottom 5% results for each language.

```{r, eval = TRUE, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}

db <- purrr::map_df(.x = list.files('../outputs/'),.f = fast_read, dir = '../outputs/') %>%
  group_by(Script) %>%
  mutate(
    top_5 = quantile(Interval, 0.95),
    bottom_5 = quantile(Interval, 0.05),
    flag_remove = if_else(Interval <= bottom_5 | Interval >= top_5, 1, 0)
  ) %>%
  filter(flag_remove != 1) %>%
  mutate(
    Order = 1:n()
  ) %>%
  ungroup()
```


```{r, eval = TRUE, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}
# graphic
db %>%
  ggplot(aes(x = Order, y = Interval, color = Script)) +
  geom_line()

db %>%
  ggplot(aes(y = Interval, color = Script)) +
  geom_boxplot()



```

```{r, eval = TRUE, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}
# table
tab_summary <- db %>%
  group_by(Script) %>%
  summarise(
    n = max(Count),
    Average_Execution = mean(Interval),
    Average_Per_Record = mean(Count/Interval/1000000000),
    Std = sd(Interval),
    Min = min(Interval),
    Max = max(Interval)
  )

DT::datatable(
  tab_summary,
  rownames = FALSE,
  options = list(dom = 'ft', scrollX = TRUE)
)

```



## Statistical Comparison

It was fit an ANOVA model to verify if the differences between the average execution times are statistically significant. 

The result is presented below:


```{r, eval = TRUE, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}

# ANOVA
resp_anova <- aov(formula = Interval ~ Script, data = db)
summary(resp_anova)

show_complement<- if_else(unlist(summary(resp_anova))["Pr(>F)1"] <= 0.05, TRUE, FALSE)

```

`r if(show_complement){"The ANOVA was significative at 5% significance level, which means that there are statistical differences in terms of averages between the excution times for the different programming languages."}`

`r if(show_complement == FALSE){"The ANOVA was not significative at 5% significance level, which means that there are no statistical difference in terms of averages between the excution times for the different programming laguanges."}`

`r if(show_complement){"To identify where these differences are it was applied the Tukey test. The Tukey test result is presente below: "}`

`r if(show_complement){" **PS:** Different letters represents statistical differences in averages terms"}`

`r if(show_complement){""}`

```{r echo = FALSE, eval = show_complement}

comp <- HSD.test(resp_anova, trt = 'Script', group = TRUE)

DT::datatable(
  comp$groups,
  rownames = TRUE,
  options = list(dom = 'ft', scrollX = TRUE)
)

```

